---
title: "Class 07"
author: "Ethan Vukovic"
date: "2026-09-16"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Demo


```{r demo}
con = DBI::dbConnect(RSQLite::SQLite(), "data/scout.db")
postings = DBI::dbReadTable(con, "scout_postings") |> tibble::as_tibble()
DBI::dbDisconnect(con)
 
jobs = postings |>
  dplyr::select(company, title, location_state, remote, category, posted_at, last_seen_at) |>
  dplyr::mutate(dplyr::across(dplyr::ends_with("_at"), as.Date),
                days_open = as.numeric(last_seen_at - posted_at))

```
## For Q1, to answer it, we need the following:f
# - number of jobs per category
# - Fraction of those jobs that are remote friendly

jobs |> 
  dplyr::group_by(category) |> 
  dplyr::summarize(
    postings = dplyr::n(), # counting the number of rows per category
    remote_share = mean(remote) |> round(3)
    
jobs |>
  dplyr::filter(category == "fulltime") |>
  dplyr::group_by(location_state) |>
  dplyr::summarise(
    postings = dplyr::n(),
    remote_share = mean(remote) |> round(3)
  ) |>
  dplyr::filter(postings >= 50) |>
  dplyr::arrange(dplyr::desc(remote_share))




